### 2019-12-20 Statistical Methods/07_hypothesis-testing.rmd
statistical methods
statistical methods

```{r, echo = T}
xbar <- 78; sigma <- 5; n <- 10
mu <- 80; alpha <- 0.05

# mu > 80 = left tail test

@@

Z <- sqrt(n)*(xbar - mu)/sigma

ifelse(Z > crit, "Fail to reject the null", "Reject the null")

@@

```{r, echo = T}
xbar <- 78; sigma <- 5; n <- 10
mu <- 80; alpha <- 0.05

# mu = 80, two-tailed test

crit <- qnorm(1 - alpha/2)

Z <- sqrt(n)*(xbar - mu)/sigma

ifelse(abs(Z) <= crit, "Fail to reject the null", "Reject the null")

@@

```{r, echo = T}
xbar <- 78; sigma <- 5; n <- 10
mu <- 80; alpha <- 0.05

xbar + qnorm(c(Lower = alpha/2, Upper = 1 - (alpha/2))) * sigma/sqrt(n)
```

@@

@@

@@

@@

@@

@@

### 7.10
### 7.11
### 7.12
### 7.13
### 7.14
### 7.15
### 7.16
### 7.17
### 7.18
### 7.19

>>>>

```{r, echo = T}
xbar <- 78; var <- 25; n <- 10
alpha <- 0.05; h0 <- 80

# greater than = left tail test

@@

Z <- sqrt(n) * (xbar - h0) / sqrt( var )

ifelse(Z < crit, "Reject the null", "Cannot reject null")
```

@@

```{r, echo = T}

# equals = two-tailed test

crit <- qnorm(alpha/2)

Z <- sqrt(n) * (xbar - h0) / sqrt( var )

ifelse(Z < crit || crit > Z, "Reject the null", "Cannot reject the null")

@@

```{r, echo = T}

xbar + qnorm(c(alpha/2, 1 - alpha/2)) * sqrt( var / n )

@@

```{r, echo = T}
pnorm(Z)
```

@@

```{r, echo = T}
2 * (1 - pnorm(Z, lower.tail = F))
```

@@

```{r, echo = T}
xbar <- 120; sigma <- 5; n <- 49
alpha <- 0.05; h0 <- 130

Z <- sqrt(n) * (xbar - h0) / sigma

ifelse( Z < crit, "Reject null hypothesis", "Cannot reject null")
```

@@

```{r, echo = T}
h0 <- 130

# two tailed test
crit <- qnorm(c(alpha/2, 1 - alpha/2))

ifelse(Z < crit[1] || Z > crit[2], "Reject null hypothesis", "Cannot Reject Null")
```

@@

```{r, echo = T}
xbar + qnorm(c(Lower = alpha/2, Upper = 1 - alpha/2)) * sigma/sqrt(n)
```

130 is not in the confidence region, reject null-hypothesis.

@@

_Yes, the hypothesis is consistent with the sample mean._

### 7.10

An electronics firm mass-produces a component for which there is a standard measure of quality. Based on testing vast numbers of these components, the company has found that the average quality is $\mu = 232, \sigma = 4$.

However, in recent years, the quality has not been checked, so management asks you to check their claim with the goal of being reasonable certain that an average quality of less than 232 can be ruled out. That is, assume that the quality is poor and in fact less than 232 with the goal of empirically establishing that this assumption is unlikely.

You get $\bar{X} = 240$ based on a sample of $n = 25$ components, and you want the probability of a Type I error to be less than 0.01.

State the null hypothesis and perform the appropriate test, assuming normality.

#### Hypothesis:

$H_0 : \mu \le 232$

$H_A : \mu \ge 232$

```{r, echo = T}
xbar <- 240; sigma <- 4; n <- 25
alpha <- 0.01; h0 <- 232

# less than = upper-tailed test

crit <- qnorm(1 - alpha)

Z <- sqrt(n) * ( xbar - h0 ) / sigma

ifelse(Z > crit, "Reject the null", "Cannot reject the null")
```

### 7.11
### 7.12
### 7.13
### 7.14
### 7.15
### 7.16
### 7.17
### 7.18
### 7.19
